---
title: "erinea_OriginalHomeworkCode_04"
author: "Erin Anderson"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Challenges: 

[1] I had a lot of trouble understanding the prop.test code. There was a lot of information within the test code and I am having a very hard time discerning what all of it means/how it all fits together, as well as picking apart which parts of the code I need to work with and which parts I can discard.

[2] I am having difficulty with the confidence intervals. I was using the code from Module 12, but it's not running effectively when I try and input it into my figure. I'm not sure what exactly is leading to this problem and could use any and all help and suggestions.

[3] I can't figure out how to add the equation for my line into gg plot. I was again using the code from Module 12, but having difficulty modifying the code to effectively include this.

[4] The beta test is also giving me a lot of difficulty. My code is returning an NA result and I'm not really sure why or how to interperet this. 

---

[1] Write a simple R function, Z.prop.test(), that can perform one- or two-sample Z-tests for proportion data, using the following guidelines:

```{r 1, include=TRUE}
p1 <- 0.5 #random
n1 <- 100 #random
p2 <- NULL
n2 <- NULL
p0 <- 0.75 #random
data.frame <- rnorm(100, mean = 50, sd = 5)
data.frame.2 <- rnorm(50, mean = 10, sd = 1)
```
I tried to make a data frame but I don't know if this is necessary/how I would use this to test my z.prop test. Also, I'm not sure what the difference between one and two sample test is, and how to incorporate it into my code or if I need seperate tests to do that.

Question 1:
```{r 2, include=TRUE}
z.prop.test <- function (x, y = NULL, alternative = "two.sided", mu = 0, sigma.x = NULL, 
    sigma.y = NULL, conf.level = 0.95) 
{
    choices <- c("two.sided", "greater", "less")
    alt <- pmatch(alternative, choices)
    alternative <- choices[alt]
    if (length(alternative) > 1 || is.na(alternative)) 
        stop("alternative must be one \"greater\", \"less\", \"two.sided\"")
    if (!missing(mu)) 
        if (length(mu) != 1 || is.na(mu)) 
            stop("mu must be a single number")
    if (is.null(sigma.x) && !is.null(x) && is.null(y)) 
        stop("You must enter the value for sigma.x")
    if (!is.null(y) && is.null(sigma.y) || is.null(sigma.x)) 
        stop("You must enter values for both sigma.x and sigma.y")
    if (!missing(conf.level)) 
        if (length(conf.level) != 1 || is.na(conf.level) || conf.level < 
            0 || conf.level > 1) 
            stop("conf.level must be a number between 0 and 1")
    if (!is.null(y)) {
        dname <- paste(deparse(substitute(x)), "and", paste(deparse(substitute(y))))
    }
    else {
        dname <- deparse(substitute(x))
    }
    xok <- !is.na(x)
    x <- x[xok]
    nx <- length(x)
    if (nx <= 2) 
        stop("not enough x observations")
    mx <- mean(x)
    estimate <- mx
    if (is.null(y)) {
        stderr <- sigma.x/sqrt(nx)
        zobs <- (mx - mu)/stderr
        method <- c("One-sample z-Test")
        names(estimate) <- c("mean of x")
    }
    else {
        yok <- !is.na(y)
        y <- y[yok]
        ny <- length(y)
        if (ny <= 2) 
            stop("not enough y observations")
        my <- mean(y)
        method <- c("Two-sample z-Test")
        estimate <- c(mx, my)
        names(estimate) <- c("mean of x", "mean of y")
        stderr <- sqrt(((sigma.x^2)/nx) + ((sigma.y^2)/ny))
        zobs <- (mx - my - mu)/stderr
    }
    if (alternative == "less") {
        pval <- pnorm(zobs)
        cint <- c(NA, zobs * stderr + qnorm(conf.level) * stderr)
    }
    else if (alternative == "greater") {
        pval <- 1 - pnorm(zobs)
        cint <- c(zobs * stderr - qnorm(conf.level) * stderr, 
            NA)
    }
    else {
        pval <- 2 * pnorm(-abs(zobs))
        alpha <- 1 - conf.level
        cint <- c(zobs * stderr - qnorm((1 - alpha/2)) * stderr, 
            zobs * stderr + qnorm((1 - alpha/2)) * stderr)
    }
    cint <- cint + mu
    names(zobs) <- "z"
    if (!is.null(y)) 
        names(mu) <- "difference in means"
    else names(mu) <- "mean"
    attr(cint, "conf.level") <- conf.level
    rval <- list(statistic = zobs, p.value = pval, conf.int = cint, 
        estimate = estimate, null.value = mu, alternative = alternative, 
        method = method, data.name = dname)
    attr(rval, "class") <- "htest"
    return(rval)
}
```
I have no clue if this is correct/what parts of this code are necessary, also I'm not sure where to input the warning
```{r 3, include=TRUE}
z.prop.test(x = c(p1, p2), y = NULL, alternative = "two.sided", mu = 0, sigma.x = NULL, 
    sigma.y = NULL, conf.level = 0.95)
```
This is confusing

Question 2:
Loading csv into R and calling the necessary columns.
```{r 4, include=TRUE}
data <- read.csv("KamilarAndCooperData.csv", sep = ",", header = TRUE, stringsAsFactors = FALSE) #importing the csv
data
longevity <- data$MaxLongevity_m #calling the column
brain_size <- data$Brain_Size_Species_Mean
my_coef <- coef(m)            # Extract coefficients of model
my_coef 
my_equation <- paste("y =",        # Extract equation of model
                     coef(m)[[1]],
                     "+",
                     coef(m)[[2]],
                     "* x")
my_equation 
library(ggplot2)
library(ggpubr)
y <- brain_size - mean(brain_size) #assigning our function to a variable per the module
x <- longevity - mean(longevity)
z <- data.frame(cbind(x, y)) #now creating the dataframe
g <- ggplot(data = data, aes(x = longevity, y = brain_size)) #creating the graph
g <- g + geom_point()
g <- g + geom_smooth(method = "lm", formula = y ~ x) + stat_regline_equation(label.x=30, label.y=310) + stat_cor(aes(label=..rr.label..), label.x=30, label.y=290)

g
```
I'm stuck on inputting the equation into the line. Suggestions?

Okay here again we are going to make another plot using the same method, but treating our varaibles with the log function in order to plot the logs of each data set.
```{r 5, include=TRUE}
data
longevity <- data$MaxLongevity_m
brain_size <- data$Brain_Size_Species_Mean
log.longevity <- log(longevity)
log.brain.size <- log(brain_size)
m <- lm(data = data, longevity ~ brain_size)
ci <- predict(m, newdata = data.frame(longevity = data$longevity), interval = "confidence",
    level = 0.95) #making a 95% CI
ci
df <- cbind(x, ci) #binding our x value with CI
names(df) <- c("x", "y", "yhat", "CIfit", "CIlwr", "CIupr")
head(df)
library(ggplot2) 
g <- ggplot(data = data, aes(x = log.longevity, y = log.brain.size))
g <- g + geom_point()
g <- g + geom_line(aes(x = log.longevity, y = CIfit), colour = "black") #This is from module 12 but it's not working
g <- g + geom_line(aes(x = log.longevity, y = CIlwr), colour = "blue")
g <- g + geom_line(aes(x = log.longevity, y = CIupr), colour = "blue")
g <- g + geom_smooth(method = "lm", formula = y ~ x)
g

```

```{r 6, include=TRUE}
my_coef <- coef(m)            # Extract coefficients of model
my_coef 
my_equation <- paste("y =",        # Extract equation of model
                     coef(m)[[1]],
                     "+",
                     coef(m)[[2]],
                     "* x")
my_equation                        # Print equation of model

```

I need to add CIs but I'm having some trouble with that.
I'm not sure how to append this using geom_text()

```{r 7, include=TRUE}
beta1 <- cor(longevity, brain_size) * (sd(brain_size)/sd(brain_size))
beta1
```
I don't know why this gives me an NA result

```{r 8, include=TRUE}
slope.test <- function(beta1) {
    g <- ggplot(data = data, aes(x = longevity, y = brain_size))
    g <- g + geom_point()
    g <- g + geom_abline(intercept = 0, slope = beta1, size = 1, colour = "blue",
        alpha = 1/2)
    ols <- sum((y - beta1 * x)^2)
    g <- g + ggtitle(paste("Slope = ", beta1, "\nSum of Squared Deviations = ",
        round(ols, 3)))
    g
}
```

